%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Vineet Shah} \\ \vspace{1pt}
    \small \underline{+1 (628)-724-1562} $|$ \href{mailto:vineet.shah@sjsu.edu}{\underline{vineetshahsjsu@gmail.com}} $|$ 
    \href{https://linkedin.com/in/vineet-shah2006}{\underline{linkedin.com/in/vineet-shah2006}} $|$
    \href{https://github.com/vineeshah}{\underline{github.com/vineeshah}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {San Jose State University}{San Jose, CA}
      {Bachelor of Science in Computer Science}{Expected: May 2027}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Data Structures \& Algorithms, Operating and Distributed Systems, Object-Oriented Programming, Formal Language and Computing}
      \resumeItemListEnd
    % \resumeSubheading
    %   {Coursera}{Online}
    %   {Machine Learning Specialization by Andrew Ng}{Dec 2024 -- Present}
    %   \resumeItemListStart
    %     \resumeItem{Gained knowledge of supervised and unsupervised learning, including classification and clustering methods}
    %     \resumeItem{Explored neural networks, regression models, and clustering algorithms}
    %   \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL EXPERIENCE-----------
\section{Technical Experience}
  \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Lifestages}}{September 2025 -- Present}
    \resumeSubSubheading
          {Software Engineering Intern}{San Francisco, CA}
          \resumeItemListStart
            \resumeItem{Architected a \textbf{Vision Dashboard} delivering real-time analytics on user engagement and predictive goal tracking.}
            \resumeItem{Shaping the platform into a \textbf{B2B SEO SaaS} with multi-tenant architecture for SEO tracking.}
            \resumeItem{Migrated backend to \textbf{Firebase Cloud Functions} to improve scalability and cut overhead.}
            \resumeItem{Built scalable data pipelines for real-time synchronization, concurrent aggregation, and intelligent pattern analysis.}
          \resumeItemListEnd
          \vspace{-4pt}
    \resumeProjectHeading
          {\textbf{San Jose State University}}{May 2025 -- August 2025}
    \resumeSubSubheading
          {Software Engineering Intern}{San Jose, CA}
          \resumeItemListStart
            \resumeItem{Built a monitoring system for internal services using \textbf{Prometheus} and \textbf{FastAPI}.}
            \resumeItem{Deployed containerized infrastructure via \textbf{Docker} and configured \textbf{NGINX} for caching and routing.}
            \resumeItem{Developed argparse- and \textbf{JSON}-based configuration logic to customize service health validation.}
            \resumeItem{Reduced detection latency by \textbf{60\%} through performance tuning, metric debugging, and live diagnostics.}
          \resumeItemListEnd

          \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{\underline{\href{https://github.com/vineeshah/ReadWMe}{ReadWMe}}} \textnormal{$|$ \emph{Nextjs, ReactJs, PostgreSQL, Groq API, Langchain, SocketIO, Puppeteer}}} { }
      \resumeItemListStart
        \resumeItem{Built a scalable backend with microservices for real-time \textbf{Reddit summarization} and interactive Q\&A, supporting thousands of users.}
        \resumeItem{Integrated \textbf{LangChain} to deliver GenAI-powered answers and adaptive queries, enhancing user engagement.}
        \resumeItem{Reduced latency by \textbf{45\%} using efficient \textbf{Socket.IO} streaming and asynchronous caching strategies.}
        \resumeItem{Implemented robust \textbf{monitoring} and optimized throughput for reliable, consistent performance.}
      \resumeItemListEnd

      \resumeProjectHeading
      {\textbf{\underline{\href{https://github.com/vineeshah/IdealMeal}{IdealMeal}}} \textnormal{$|$ \emph{Flask, ReactJs, GeminiAPI, MongoDB, Google Places API, Tailwindcss}}} { }
      \resumeItemListStart
        \resumeItem{Developed an AI meal recommender using \textbf{GenAI} and cloud APIs to provide personalized, location-based suggestions.}
        \resumeItem{Leveraged \textbf{Gemini API} for natural language understanding and accurate user intent detection.}
        \resumeItem{Built a scalable backend with \textbf{MongoDB} and \textbf{Places API} for dynamic, adaptive results.}
        \resumeItem{Improved reliability and performance with advanced \textbf{caching}, \textbf{load balancing}, and automated CI/CD pipelines.}
      \resumeItemListEnd

      \resumeProjectHeading
      {\textbf{\underline{\href{https://github.com/vineeshah/SplitFree}{SplitFree}}} \textnormal{$|$ \emph{Flask, ReactJS, PostgreSQL, TailwindCSS}}} { }
      \resumeItemListStart
        \resumeItem{Designed distributed algorithms for efficient \textbf{debt settlement} across user groups, optimizing for speed and accuracy.}
        \resumeItem{Optimized \textbf{database queries} and indexing to enable fast computation and scalable performance.}
        \resumeItem{Built secure \textbf{REST APIs} with automated validation, comprehensive testing, and robust error handling.}
        \resumeItem{Simulated \textbf{concurrent loads} to ensure system resilience and reliability under real-world conditions.}
      \resumeItemListEnd

      \resumeProjectHeading
      {\textbf{\underline{\href{https://github.com/vineeshah/Fleetsure}{Fleetsure}}} \textnormal{$|$ \emph{Java, OOP, Layered Architecture}}} { }
      \resumeItemListStart
        \resumeItem{Developed a modular vehicle management system using \textbf{layered architecture} for maintainability and scalability.}
        \resumeItem{Applied advanced \textbf{OOP principles} to create a reusable, extensible codebase for rapid feature development.}
        \resumeItem{Simulated business workflows for \textbf{inventory} and \textbf{customer management}, focusing on operational reliability.}
        \resumeItem{Optimized efficiency for scalable deployment in \textbf{distributed setups} and resource-constrained environments.}
      \resumeItemListEnd
      
    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages}{: Python, Java, JavaScript, Go, C++, C, TypeScript, SQL} \\
    \textbf{Cloud \& Distributed Systems}{: AWS (EC2, S3, Lambda), Docker, Nginx, Prometheus, SocketIO, REST APIs} \\
    \textbf{Frameworks \& Tools}{: Flask, ReactJS, NextJs, Django, FastAPI, TailwindCSS, Spring Boot, Git, CI/CD} \\
    \textbf{Databases}{: PostgreSQL, MongoDB, MySQL, Redis (SQL \& NoSQL)} \\
    \textbf{AI \& GenAI APIs}{: OpenAI API, Gemini API, LangChain, RAG Pipelines, Groq API, Google Places API}
    }}
\end{itemize}


%-------------------------------------------
\end{document}